\chapter{Advanced Sentence}
\begin{itemize}
    \item Different people have different views on opportunity. Some people think that
     there are few opportunities in the world, \uline{while} others argue that everybody will
      have some kind of opportunity along his life route.
    \item \uline{Those who} are in favor of the Internet claim that it has a lot of advantages.
    \item \uline{Only when} all of us join in the efforts of eliminating cheating at all levels
    \uline{can we} expect to have a cleaner society and a more beautiful future.
    \item He will make the right choice \uline{if} he knows his goal in life and how to make 
    decisions according to the goal.
    \item First of all, the main financial support comes from parents and other family
     members. For all the years \uline{it is} they \uline{who} give the student courage and 
     determination to hold on and excel.
    \item \uline{How shall I} sum up my feeling upon hearing the news of this new test?
    \item To begin with, \uline{although} you may feel anxious to finish the work when 
    the deadline is drawing near, it doesn't mean you can finish your job with 
    high quality.
    \item We can \uline{never} wish to realize our dream of a cleaner and more beautiful
     environment \uline{until} all of us take actions to build, protect and take care of it.
    \item Taking all these factors into consideration, we may safely come to the conclusion
     that \uline{there is no such thing as} destined fate in our life.
    \item For another, if a person is diligent and determined, he will realize his
     dream no matter how poor, humble or unlucky he may be.
    \item We \uline{cannot emphasize the importance of} protecting our eyes \uline{too much}.
    \item \uline{There is no need for} you \uline{to} bring more food.
    \item \uline{By taking} exercise, we \uline{can} always stay healthy.
    \item Listening to music \uline{enables us to feel} relaxed.
    \item \uline{On no account can we ignore} the value of knowledge.
    \item What will happen to sb.? 
    \item \uline{For the past two years},I have been busy preparing for the examination.
    \item It pays to help others
    \item The progress of thee society \uline{is based on} harmony.
    \item We should \uline{do our best to} achieve our goal in life.
    \item We should \uline{spare no effort/make every effort to} beautify our environment
    \item Taking exercise \uline{is closely related to} health
    \item We should \uline{get into the habit of} keeping good hours.
    \item What an important thing it is to keep our promise!
    \item How important a thing it is to keep our promise!
    \item Smoking \uline{has a great influence on} our health.
\end{itemize}